A Bayesian search to find \\high-mass black holes in LIGO data

### 2020-08-21 main.tex
update images

 In this paper we utilise a Bayesian method to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).  We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance. \\

The remainder of this paper is structured as follows. We outline our analysis methods, including details of our Bayesian  in Section~\ref{sec:method}. We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.

@@

@@

a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors. A signal-coherence test such as the Bayesian coherence ratio (\bcr) \cite{bcr_paper} provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise. Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}. The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors. \\

% PyCBC asks for the 5 citations:
% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors. $\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_Ni}$ or a glitch $\mathcal{H_Gi}$. The \bcr is given by
\begin{equation}
BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
\end{equation}
where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_Ni}$, and $\mathcal{H_Gi}$. $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.

@@

high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.  At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers. For the trigger to be considered a  candidate event by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}. The simulated signal events are artificially created by injecting signals into the detector data. Similarly, \pycbc artificially constructs the background, signal-free, events by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.

>>>>

 In this paper we utilise a Bayesian method, called the\bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).  We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance. \\

The remainder of this paper is structured as follows. We outline our analysis methods, including details of the \bcr in Section~\ref{sec:method}. We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.

@@

\subsection{The Bayesian Coherence Ratio}

@@

Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors. $\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_N}$ or a glitch $\mathcal{H_G}$. The \bcr is given by
\begin{equation}
BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
\end{equation}
where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$. $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$. As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximize the \bcr distributions for background data (signal-free data) and simulated signals $\cite{BCR1}.

 provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise. Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}. The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors. \\

@@

% PyCBC asks for the 5 citations:
% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.  At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers. For the trigger to be considered a  candidate event by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}. The simulated signal events are artificially created by injecting signals into the detector data. Similarly, \pycbc artificially constructs the background, signal-free, events by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.
